Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
...

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\cdot{} l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $i = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+k] = 1$. Taking into account this correspondence between messages $y$ in $\mathcal{M}$ and their clustered representation $x$, we will now also consider $x$ as messages.

@@

		We make a small modification the classic retrieving rule to fully exploit the local regularity of the code (constant weight of $a$). We keep activated all units that achieve a score equal or greater than the $w$-th score. (where $w$ is a positive integer parameter)

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural one with $w = 1$ as well).
		%Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :

@@

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula). The information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.

@@

	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.

	\subsubsection{Simulations}
		Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent,

		Simulations agree with the analytical results for error rate, see Figure \ref{erasuresth}. We observe a small shift.

	For one iteration (for erasures, not for errors), "winner takes all" is the same as "$a$-winners take all".

	For multiple iterations $a$-winners take all is a significant improvement.
	%The variant of the rule significantly improves the retrieval rate over multiple iterations. (For one iteration, is is the same as taking only maximum scores.)

@@

		Figure \ref{comperth} shows improvements in capacities over unipartite cliques network. The more the problem is difficult, the more redundancies introduced by multipartite cliques are useful.

>>>>

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\cdot{} l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $i = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, unit $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+k] = 1$. Taking into account this correspondence between messages $y$ in $\mathcal{M}$ and their clustered representation $x$, we will now also consider $x$ as messages.

@@

		We make a small modification the classic retrieving rule to fully exploit the local regularity of the code (constant weight of $a$). We keep activated all units that achieve a score equal or greater than the $w$-th score. (where $w$ is a positive integer parameter). $w = 1$ amounts to taking the maximum and so is exactly the same as the classic retrieving rule.

@@

		Intuitively the choice of $w = a$ is optimal, as each cluster should eventually contain exactly $a$ active units to at least represent a symbol in $\mathcal{A}$. %(it it is the most natural one with $w = 1$ as well).
		%Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :

@@

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula). The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.

@@

	The maximum ratio of information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.

	\subsubsection{Simulations}

		Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent,

		Simulations agree with the analytical results for error rate, albeit we can observe a small shift, see Figure \ref{erasuresth}. For one iteration, as long as the parameter $w$ is between $1$ and $a$, there is no effect on retrieving. However for $4$ iterations, the choice of $w = a$ allows a shift of about $5000$ messages stored on top of those stored for $w = 1$. The variant rule can thus be considered a significant improvement over the classic one for multipartite clique networks (recall that $w = 1$ amounts to the classic retrieving rule).

	%For one iteration (for erasures, not for errors), "winner takes all" is the same as "$a$-winners take all".

	%For multiple iterations $a$-winners take all is a significant improvement.
	%The variant of the rule significantly improves the retrieval rate over multiple iterations. (For one iteration, is is the same as taking only maximum scores.)

@@

		Thanks to the efficiency defined in the previous section, we can easily compare distinct choices of parameters $a$ (we now take $w = a$ since it is the most efficient choice in practice) over distinct number of erased clusters. Figure \ref{comperth} shows improvements in efficiencies over parameter $a =1$. The more difficult the problem is, the more redundancies introduced by multipartite cliques are useful.
